---
title: "Slidy Outro"
output: slidy_presentation
css: "sample-css.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r data, echo = TRUE}
# you need to load a datafile first before
# you can use it
load("sampledata.RData")
# show code with results
# if echo = TRUE, the code will be seen
summary(b$Trip.Total, 2)
# you can even plot on the slide
hist(b$Trip.Total)

```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## New Slide with Code Chunk
```{r new_code_chunk, echo = FALSE}

```

## Slide with embedded code

The square root of 69 is `r sqrt(69)`
